PANCHANGE_analysis

### 2020-09-03 PANCHANGE_analysis.Rmd
Corrected dataset namings, required after the exclusion chunk was moved.

Diagnoses analyses
```{r dat.mhd - Vectors with sum_score_cols}
sum_score_cols <- dat.mhd %>%
  select(contains("sum_score")) %>%
  select(-ends_with("raw")) %>%
  colnames()

@@

phq.sum_score_cols <- dat.mhd %>%
  select(contains("phq")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  select(-contains("8items")) %>%
  colnames()

@@

gad.sum_score_cols <- dat.mhd %>%
  select(contains("gad")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

ocir.sum_score_cols <- dat.mhd %>%
  select(contains("ocir")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

pcl.sum_score_cols <- dat.mhd %>%
  select(contains("pcl")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

```{r Vectors with diff_score_cols}
diff_score_cols <- dat.mhd %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

phq.diff_score_cols <- dat.mhd %>%
  select(contains("phq")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

gad.diff_score_cols <- dat.mhd %>%
  select(contains("gad")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

ocir.diff_score_cols <- dat.mhd %>%
  select(contains("ocir")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

dat <- dat.raw %>%
  mutate(
    Disorder_hierarchical_psychosis =
      recode_factor(
        Disorder_hierarchical_psychosis_numeric,
        `0` = "Controls",
        `1` = "Anxiety disorders",
        `2` = "Eating disorders",
        `3` = "OCDs",
        `4` = "PTSD",
        `5` = "Depressive disorders",
        `6` = "Bipolar disorders",
        `7` = "Psychotic disorders"
      )
  )

>>>>

Diagnoses analyses
```{r dat.mhd - Vectors with sum_score_cols}
sum_score_cols <- dat.raw %>%
  select(contains("sum_score")) %>%
  select(-ends_with("raw")) %>%
  colnames()

@@

phq.sum_score_cols <- dat.raw %>%
  select(contains("phq")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  select(-contains("8items")) %>%
  colnames()

@@

gad.sum_score_cols <- dat.raw %>%
  select(contains("gad")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

ocir.sum_score_cols <- dat.raw %>%
  select(contains("ocir")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

pcl.sum_score_cols <- dat.raw %>%
  select(contains("pcl")) %>%
  select(contains("sum_score")) %>% 
  select(-ends_with("raw")) %>%
  colnames()

@@

```{r Vectors with diff_score_cols}
diff_score_cols <- dat.raw %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

phq.diff_score_cols <- dat.raw %>%
  select(contains("phq")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

gad.diff_score_cols <- dat.raw %>%
  select(contains("gad")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

ocir.diff_score_cols <- dat.raw %>%
  select(contains("ocir")) %>%
  select(contains("diff_score")) %>% 
  colnames()

@@

dat <- dat %>%
  mutate(
    Disorder_hierarchical_psychosis =
      recode_factor(
        Disorder_hierarchical_psychosis_numeric,
        `0` = "Controls",
        `1` = "Anxiety disorders",
        `2` = "Eating disorders",
        `3` = "OCDs",
        `4` = "PTSD",
        `5` = "Depressive disorders",
        `6` = "Bipolar disorders",
        `7` = "Psychotic disorders"
      )
  )
